Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
updated the table

\todo{Zack: Mau, check this first sentence}
Since we are interested in the success of the job status of each commit, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and not successful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.
At this point we had a 3:1 successful to 
not successful ratio in the rows of the data sets.

@@

\hline
\end{tabular}
\\
\center
  \caption{Comparison of predictive power by running 10-fold
    cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column). The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}}   
\end{table*}

>>>>

\todo{Zack: Mau, check this paragraph}
Since we are interested in the success of the job status of each commit, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and not successful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, we removed the
commit from the data set.
\todo{confirm that this number doesn't change}
At this point we had a 3:1 successful to 
not successful ratio in the rows of the data sets.

@@

\hline
\end{tabular}
\\
\center
	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
    cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column). 
	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
	%Zack: the above sentence isn't true for the second row.
	}   
\end{table*}
